Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-21 Paper/paper.tex
Have diagram of inequalities

In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), we have:

@@

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
            \foreach \x in {0,8}
            {\coordinate (origin) at (\x,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\(\bar\lambda_{K_{\NH}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {Occupancy at NH};
                % lambda
                \draw ($(origin) + (0,4)$) -- ($(origin) + (2,4)$) -- ($(origin) + (2,2)$) -- ($(origin) + (5,2)$);
                \node at ($(origin) + (1,3.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
                \node at ($(origin) + (3.5,1.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
                % Effect of KNH
                \draw [dashed] ($(origin) + (0,4)$) -- ($(origin) + (4,4)$) -- ($(origin) + (4,2)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,4)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,4)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\NH}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\NH}+1\)};
            };
        \end{tikzpicture}
    \end{center}
    \caption{The effect of \(K_{\NH}\) on \(\bar \lambda\).}\label{fig:effect_of_KNH_on_arrival_rate}
\end{figure}

>>>>

In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), this gives:

@@

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
            \foreach \x in {0,9}
            {\coordinate (origin) at (\x,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\(\bar\lambda_{K_{\NH}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {Occupancy at NH};
                % lambda
                \draw ($(origin) + (0,4)$) -- ($(origin) + (2,4)$) -- ($(origin) + (2,2)$) -- ($(origin) + (5,2)$);
                \node at ($(origin) + (1,3.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
                \node at ($(origin) + (3.5,1.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
                % Effect of KNH
                \draw [dashed] ($(origin) + (0,4)$) -- ($(origin) + (4,4)$) -- ($(origin) + (4,2)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,4)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,4)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\NH}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\NH}+1\)};
            };
        \end{tikzpicture}
    \end{center}
    \caption{The effect of \(K_{\NH}\) on \(\bar \lambda\).}\label{fig:effect_of_KNH_on_arrival_rate}
\end{figure}

Using (\ref{equ:UNH_as_a_function_of_KRG}) and (\ref{equ:UNH_as_a_function_of_KNH}) the general inequalities associated with \(U_{\NH}(K_{\NH}, K_{\RG})\) are summarised in Figure \ref{fig:variation_of_UNH}.

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
            % Coordinate system
            \draw [very thick, ->] (0,0) -- (0,6) node[anchor=south east] {\(K_{\RG}\)};
            \draw [very thick, ->] (0,0) -- (7,0) node[anchor=north west] {\(K_{\NH}\)};

            % Points
            \foreach \x in {1,2,3,4,5,6}
                {
                \foreach \y in {1,2,3,4,5}
                    {
                        \node at (\x, \y) {\textbullet};
                    };
                };

            % Negative region
            \draw[rounded corners, dashed, thick] (.5,5.5) --
              ++(5, 0) -- ++(0,-1) -- ++(-1, 0)  -- ++(0,-1) -- ++(-1,0) --
              ++(0, -2) -- ++(-2,0) -- ++(-1, 0) -- cycle;
            \draw [<-, thick] (3.25,4.75) -- (4.75,6) node[anchor= south west] {\(U_{\NH}\leq t\)};

            % Vertical inequalities
            \foreach \x in {1,2,3,4,5,6}
                {
                \foreach \y in {1.5,2.5,3.5,4.5}
                    {
                        \node at (\x, \y) [blue!100, rotate=90] {\textbf{\(\geq\)}};
                    };
                };

            % Horizontal inequalities
            \foreach \x in {1.5,2.5,3.5,4.5,5.5}
                {
                \foreach \y in {1,2,3,4,5}
                    {
                        \node at (\x, \y) [red!100] {\textbf{\(\leq\)}};
                    };
                };
        \end{tikzpicture}
    \end{center}
    \caption{Values \(U_{\NH}\).}\label{fig:variation_of_UNH}
\end{figure}

As \(\U_{\NH}\) increases from the lowest value (top left in Figure  \ref{fig:variation_of_UNH}) to the highest (bottom right in Figure \ref{fig:variation_of_UNH}) the value of \(U_{\NH}-t\) will change sign (from negative to positive).
